---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# elaacoustics
Analytical Tools for ILK's ELA Acoustic Surveys

<!-- badges: start -->
![R](https://img.shields.io/badge/r-%23276DC3.svg?style=for-the-badge&logo=r&logoColor=white)
![GitHub](https://img.shields.io/badge/github-%23121011.svg?style=for-the-badge&logo=github&logoColor=white)
<!-- badges: end -->

## Installation
 
This package is not available at this time on CRAN. You can install `elaacoustics` from the GitHub repository using `devtools::install_github()`.

``` {r install, eval = FALSE}
devtools::install_github("HoldenJe/elaacoustics")
```

## Example

This is an example of how to use the basemaps for each lake.
```{r example1, warnings = FALSE}
library(elaacoustics)
library(ggplot2)
basemap_lake379
```

This is an example of how to add a point to the basemap of the lake.
```{r example2}
basemap_lake379 + 
  geom_point(aes(x = -93.799462, y = 49.708170), pch = 13, size = 4)
```

This is an example of how to combine multiple lake files on a single plot and add customization.
```{r example3}
ggplot()+ 
  geom_sf(data = shape_lake379, fill = 'blue') + 
  geom_sf(data = shape_lake259, fill = 'blue') +
  geom_point(aes(x = -93.799462, y = 49.708170), pch = 13, size = 4, colour = "yellow") +
  theme_bw() +
  ylab("Latitude") + xlab("Longitude") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
